---
title: "Recruit restaurant visitor competition EDA"
output:
  html_document:
    toc: yes
  html_notebook:
    toc: yes
---

# Introduction

This notebook is going to focus on analysing the data for the recruit restaurant visitor prediction problem on kaggle.
See here for more information: https://www.kaggle.com/c/recruit-restaurant-visitor-forecasting

## Other useful analyses

* https://www.kaggle.com/headsortails/be-my-guest-recruit-restaurant-eda
* https://www.kaggle.com/captcalculator/a-very-extensive-recruit-exploratory-analysis
* https://www.kaggle.com/breakfastpirate/weeks-before-after-golden-week-2016
* https://www.kaggle.com/timolee/feeling-hungry-a-beginner-s-guide-to-arima-models

```{r, libs, message = FALSE, warning = FALSE}
library(ggplot2)
library(ggTimeSeries)
library(tidyverse)
library(lubridate)
library(scales)
```

```{r, read_data, echo = FALSE}
data_path <- 'F:/Nerdy Stuff/Kaggle/Recruit'
setwd(data_path)

air_res <- read_csv('air_reserve.csv')
air_store_info <- read_csv('air_store_info.csv')
air_visit_data <- read_csv('air_visit_data.csv')

date_info <- read_csv('date_info.csv')
hpg_res <- read_csv('hpg_reserve.csv')
hpg_store_info <- read_csv('hpg_store_info.csv')
samp_sub <- read_csv('sample_submission.csv')
store_id <- read_csv('store_id_relation.csv')

```

# Analysis

## Air dataset

```{r}

air_res <- air_res %>% 
  mutate(visit_hour = hour(visit_datetime),
         res_hour = hour(reserve_datetime),
         time_after_book_visit = difftime(visit_datetime, reserve_datetime, units = 'hours'),
         year_reserve = year(reserve_datetime),
         year_visit = year(visit_datetime)) %>% 
  mutate(hours_after_book_visit = as.integer(time_after_book_visit))

glimpse(air_res)

g1 <- ggplot(air_res, aes(x = as.Date(visit_datetime), y = reserve_visitors)) +
  geom_jitter(alpha = 0.4) + geom_smooth() 

g1 + theme_minimal() + scale_x_date(date_breaks = '2 months') + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(x = 'Date of visit',
       y = 'Number of people in reservation',
       title = 'Air reservations')

g1 <- air_res %>% 
  filter(hours_after_book_visit < 168) %>% 
  ggplot(aes(x = hours_after_book_visit)) + geom_histogram()

g1 + theme_minimal() + labs(y = 'Count',
                            x = '',
                            title = 'Hours between booking and going to the restaurant') +
  scale_y_continuous(breaks = seq(0, 20000, by = 2500), limits = c(0, 20000), labels =comma)

g1 <- ggplot(air_res, aes(x = as.Date(visit_datetime), y = hours_after_book_visit)) +
  geom_jitter(alpha = 0.4) + geom_smooth() 

g1 + theme_minimal() + scale_x_date(date_breaks = '2 months') + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(x = 'Date of visit',
       y = 'Hours between booking and going to the restaurant',
       title = 'Does the amount of time between booking and going change over time?',
       subtitle = 'Maybe, but there is definitely a few weird days..')

```

### Observations:

* There's quite a large break in the dataset from August 2016 to October
* Hours between booking and going to the restaurant have a few days with very weird patterns
* From Aprilish onwards there is no reservations with very bookings with low hours between booking and turning up

```{r}

g1 <- ggplot(air_res, aes(y = hours_after_book_visit, x = reserve_visitors)) + 
  geom_jitter(alpha = 0.5) + geom_smooth()
  
g1 + theme_minimal() + labs(y = 'Hours between booking and going to the restaurant',
                            x = 'Number of people on the reservation',
                            title = 'Relationship between booking size and time lag between book and visit',
                            subtitle = 'Nice looking positive trend') + 
  scale_y_continuous(breaks = seq(0, 10000, by = 1000), limits = c(0, 10000), labels = comma)

```

```{r}

g1 <- air_res %>% 
  filter(visit_datetime > "2017-04-15") %>% 
           ggplot(aes(x = as.Date(visit_datetime), y = hours_after_book_visit)) +
  geom_jitter(alpha = 0.4) + geom_smooth() 

g1 + theme_minimal() + scale_x_date(date_breaks = '5 days') + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(x = 'Date of visit',
       y = 'Hours between booking and going to the restaurant',
       title = 'Looks like new resevations arent included after April the 20th')

```