---
title: "Recruit restaurant visitor competition EDA"
output: 
  html_notebook:
    toc: true
---

# Introduction

This notebook is going to focus on analysing the data for the recruit restaurant visitor prediction problem on kaggle.
See here for more information: https://www.kaggle.com/c/recruit-restaurant-visitor-forecasting

## Other useful analyses

* https://www.kaggle.com/headsortails/be-my-guest-recruit-restaurant-eda
* https://www.kaggle.com/captcalculator/a-very-extensive-recruit-exploratory-analysis
* https://www.kaggle.com/breakfastpirate/weeks-before-after-golden-week-2016
* https://www.kaggle.com/timolee/feeling-hungry-a-beginner-s-guide-to-arima-models

```{r, libs, message = FALSE}
library(ggplot2)
library(ggTimeSeries)
library(tidyverse)

```

```{r, read_data}
data_path <- 'F:/Nerdy Stuff/Kaggle/Recruit'
setwd(data_path)

air_res <- read_csv('air_reserve.csv')
air_store_info <- read_csv('air_store_info.csv')
air_visit_data <- read_csv('air_visit_data.csv')

date_info <- read_csv('date_info.csv')
hpg_res <- read_csv('hpg_reserve')
hpg_store_info <- read_csv('hpg_store_info.csv')
samp_sub <- read_csv('sample_submission.csv')
store_id <- read_csv('store_id_relation.csv')

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

